title: "Golden Goals Analytics"
author: Vanessa Menegassi
source: Martin (2016)
data: 2021-22 Champions League
---

# Analyzing Champions League Goals Scored #

## Data
https://fbref.com/en/comps/8/stats/Champions-League-Stats
Player Standard Stats 2021-2022 Champions League
Filter by goals
Click in share and export
Modify and export

Select the variables:
-	Player
-	Position
-	Squad
-	Playing time
-	Goals
-	Assists
-	Goals scored per 90 min
-	Assists per 90 min 
-	Expected Goals
-	Expected Assists
-	Expected Goals per 90 min
-	Expected Assists per 90 min

Download as CSV (2 sheets 500 + 230) limits to 500 lines
Merge 2 documents

## Analysis

## 01 Import Dataset "Golden.Goals", install and run packages.

```{r}

Golden.Goals <- read.csv("~/Documents/GitHub/Golden Goals/Golden Goals.csv", header=TRUE, sep=";")

install.packages("dplyr")
install.packages("rstatix")
install.packages("tidyverse")
library(dplyr)
library(rstatix)
library(tidyverse)

```

## 02 Checking the structure of the data

```{r}

str(Golden.Goals)
summary(Golden.Goals)

```

## 03 Grouping players by position

```{r}
                        
Golden.Goals$Position[Golden.Goals$Position == "FW,MF" | Golden.Goals$Position == "MF,FW" | Golden.Goals$Position == "DF,FW" | Golden.Goals$Position == "FW,DF"| Golden.Goals$Position == "MF,DF" | Golden.Goals$Position == "DF,MF"] <- "HI"

```

## 04 Creating new data frames for the positions

```{r}

Forwards <- Golden.Goals %>% dplyr::filter(Position == "FW")
Midfielders <- Golden.Goals %>% dplyr::filter(Position == "MF")
Defenders <- Golden.Goals %>% dplyr::filter(Position == "DF")
Goalkeepers <- Golden.Goals %>% dplyr::filter(Position == "GK")
Hybrids <- Golden.Goals %>% dplyr::filter(Position == "HI")

```

## 05 Building a simple regression model

```{r}

GoalsPositionModel1 <- lm(Goals ~ Position, data = Golden.Goals)
summary(GoalsPositionModel1)

```

## 06 Comparing goals by position (T_Test)

```{r}

GoalsPosition <- Golden.Goals %>%
  t_test(Goals ~ Position) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()
view(GoalsPosition)

```

## 07 Count data using a Poisson regression. Uses a log link to model data.

```{r}

GoalsbyPositionsPoissonModel1 <- glm(Goals ~ Position,
data = Golden.Goals, family = poisson)
summary(GoalsbyPositionsPoissonModel1)

```

## 08 Creating simple visualizations by position

```{r}

with(Golden.Goals, boxplot(Goals ~ Position,
xlab = "Soccer Player Position", ylab = "Goals",
names = c("Defender", "Forward", "Goalkeeper", "Hybrid", "Midfielder"),
col = "gray92",
main = "Number of Goals by Player Position (Champions League)",
cex.lab = 1.2))

```

### TASKS: 
1. Do the same process with all the other independent variables, comparing by position;
2. Find better ways to present results (visualizations) with other packages or graphics;
3. Whats the strength of the relationship between Goals and xG? What about Assists and xA?

